---
title: "BBets Project"
author: "Sammy"
date: "1/31/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The question is how much money is won/lost on a bet that at least two people have the same b'day in a class of 35.  Instructor wagers 2:1 

Instuctor has done this 15 times,  
1.what is his expected win/loss amount,  
2. how much would the instructor have to wager to make the bet fair?  
3. how many students would have to be in the class for a 2:1 bet to be fair?   
 
 
```{r}
days = 1:365

nStudents = 29
nBets = 1000
saveArray=vector('numeric')
for(k in 1:1000){
  bank = 0
  for(i in 1:nBets){
    sampleClass = sample(days, 29, replace = TRUE)

    repeats = length(unique(sampleClass))
    if (repeats == 29) bank = bank - 2
    else bank = bank + 1
  }
saveArray[k]= bank
}

```
 
histogram of bank amounts.   

```{r}
hist(saveArray)
```

Answer questions #1

with 35 students and payoff of 2:1, Dr. J makes on average $235  

```{r}
print('average amt:')
print(mean(saveArray))
```


the amount of $ Dr J should pay 35.00

Answer questions #2


looks like $4.50  is about right

# Answer to question 3

around 29 students